A seamless, client-centric programming model for type safe web applications

### 2014-03-01 paper.tex
Add real world applications to future work.

\subsection{The chatbox, revisited}

@@

>>>>

\subsection{The chatbox, revisited}\label{sec:chatboxrevisited}

@@

\paragraph{Real world applications} As Haste.App is quite new and experimental,
it has yet to be used in the creation of large scale applications. While we
have used it to implement some small applications, such as a spaced repetition
vocabulary learning program and a more featureful variant on the chatbox
example given in section \ref{sec:chatboxrevisited}, further investigation of
its suitability for larger real world applications through the development of
several larger scale examples is an important area of future work.
